---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plotBart

<!-- badges: start -->
[![R-CMD-check](https://github.com/joemarlo/plotBart/workflows/R-CMD-check/badge.svg)](https://github.com/joemarlo/plotBart/actions)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](/LICENSE.md)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- badges: end -->

plotBart is a supplemental plotting package to [bartCause](https://github.com/vdorie/bartCause) and [thinkCausal](https://github.com/gperrett/thinkCausal_dev).

```{r example, fig.width=8, message=FALSE, warning=FALSE, out.width = "75%", fig.align="center"}
library(plotBart)
data(lalonde, package = 'arm')
confounders <- c('age', 'educ', 'black', 'hisp', 'married', 'nodegr')

# fit BART model
model_results <- bartCause::bartc(
  response = lalonde[['re78']],
  treatment = lalonde[['treat']],
  confounders = as.matrix(lalonde[, confounders]),
  estimand = 'ate',
  commonSup.rule = 'none',
  verbose = FALSE
)

# plot common support
plot_diagnostic_common_support(.model = model_results)

# plot overlap by variable
plot_overlap_vars(
  .data = lalonde,
  treatment_col = 'treat',
  confounder_cols = confounders,
  plt_type = 'Histogram'
) + labs(subtitle = 'My informative subtitle')
```


## Installation

plotBart is currently in development and is available to test by installing via:

``` r
# install.packages("devtools")
devtools::install_github("joemarlo/plotBart")
```

## Dev to-do
- Write vignette
- Remove functions from thinkCausal repo
- Fix issue in plot_variable_importance. See TODO line 46

### Test coverage

```{r echo=FALSE}
covr::package_coverage()
```

